Dragonfly Territory Ananlysis

### 2020-12-03 analysis/analysisSS.Rmd
typo in figure, needed to by fixed in analysis, manuscript and .png replaced with corrected spelling

plot(pNymphulaCompAY$YEAR, pNymphulaCompAY$pNymphulaAbundance, main = "Pyrrhosa nymphula", xlab = "Year", ylab = "Abundance")
abline(lm (pNymphulaCompAY$pNymphulaAbundance ~ pNymphulaCompAY$YEAR), col="red")

>>>>

plot(pNymphulaCompAY$YEAR, pNymphulaCompAY$pNymphulaAbundance, main = "Pyrrhosoma nymphula", xlab = "Year", ylab = "Abundance")
abline(lm (pNymphulaCompAY$pNymphulaAbundance ~ pNymphulaCompAY$YEAR), col="red")
